---
title: Filtering with crosstalk
date: 2021-01-22
section: tests
summary: "Filtering interactive content with crosstalk"
weight: 400
---

This is a test of an interactive `RMarkdown` document within the govuk-hugo theme, on `r Sys.Date()` using [`{crosstalk}`](https://rstudio.github.io/crosstalk/) to interactively filter data.

## Prepare data

`{crosstalk}` is an R package that supports interactive Rmarkdown files, it is particularly useful for `govukhugo` as it can support client-side data processing and therefore enables complex interactivity without relying on Shiny. To use `{crosstalk}` we initiate a `SharedData` object by a call to `crosstalk::SharedData$new()`.

```{r setup, include = FALSE}
penguins_sd <- crosstalk::SharedData$new(palmerpenguins::penguins)
```

Compatability issues means this only works with tables (via `govukhgo::govuk_datatable()`) and not yet with interactive plots (via `{plotly}`), it has not yet been tested with interactive maps (via `{leaflet}`).

## Filtering the table

Once enabled we can use `{crosstalk}` to filter the data object, and to link tables and plots. At present only the `filter_select()` filters are supported for use in `govukhugo`.

``` {r}
fs_species <- crosstalk::filter_select(
  id = "filter-species",
  label = "Penguin species",
  sharedData = penguins_sd,
  group = ~species,
  multiple = FALSE
)

fs_island <- crosstalk::filter_select(
  id = "filter-island",
  label = "Island",
  sharedData = penguins_sd,
  group = ~island,
  multiple = TRUE
)
```

`{crosstalk}` is designed to work with the [Bootstrap CSS framework](https://getbootstrap.com/) which does not work well with the GOV.UK Design System, therefore the filters should be wrapped inside a call to `govukhugo::unstrap()` to remove the Bootstrap dependencies.

```{r selector-example, eval=FALSE}
govukhugo::unstrap(fs_species)
govukhugo::unstrap(fs_island)
```


::::{.govuk-grid-row .data-row}

:::{.govuk-grid-column-one-quarter .filter-controls .govuk-body-s}

<span class="govuk-heading-s">Filters</span>

```{r selectors, echo=FALSE}

govukhugo::unstrap(fs_species)

govukhugo::unstrap(fs_island)

```
<span style="display:block;clear:both;"></span>
:::

:::{.govuk-grid-column-three-quarters .tbl-display}
```{r penguin-table, echo=FALSE}
govukhugo::govuk_datatable(
  penguins_sd,
  col_names = c("Species", "Island", "Bill length (mm)", "Bill depth (mm)",
                "Flipper length (mm)", "Body mass (g)", "Sex", "Year"),
  page_length = 10,
  search = FALSE
)
```
:::

::::
