---
title: Interactive R Markdown
date: 2021-01-22
section: tests
weight: 900
---

This is a test of an interactive `RMarkdown` document within the govuk-hugo theme, on `r Sys.Date()`.

## Testing DT

This is a test of the [`{DT}`](https://rstudio.github.io/DT/) package that implements interactive tables via the [DataTables jQuery plugin](https://datatables.net/examples/styling/jqueryUI.html)

```{r}
new_cars <- tibble::rownames_to_column(mtcars, var = "model")
govukhugo::govuk_datatable(new_cars)
```

## Testing Plotly
This is a test of `plotly::ggplotly()` which uses the [Plotly R package and JavaScript Library](https://plot.ly/r/) to convert `{ggplot2}` charts into interactive charts

```{r}
p <- ggplot2::ggplot(mtcars, ggplot2::aes(x = mpg, y = disp)) +
  ggplot2::geom_point()

plotly::ggplotly(p)

```


## Testing leaflet
This is a test of the [`{leaflet}`](https://rstudio.github.io/leaflet/) package that produces interactive maps using [leaflet.js](https://leafletjs.com/).

```{r}
m <- leaflet::leaflet()
m <- leaflet::addTiles(m)
m <- leaflet::addMarkers(m, lng = -0.12768, lat = 51.50739)
m
```

